Soling at the 2000 Summer Olympics

### 2020-07-22 inst/f1points.Rmd
name 2017 variables to foo2017

```{r, label=calcpoints, echo=FALSE, cache=TRUE}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points_real <- p
points_inaugural <- c(8,6,4,3,2)
dp <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp <- sort(dp,decreasing=TRUE)
dp[] <- seq_along(dp)
m <- maxp(H2017)
m <- sort(m,decreasing=TRUE)
m[] <- seq_along(m)
```

@@

```{r,label=likevspoints,cache=TRUE,echo=FALSE,fig.cap="Ordering of the \\label{orderingbypointsandlikelihood} top-ranked 11 drivers in the 2017 Formula 1 season.  Horizontal axis gives official (points-based) order, and the vertical axis gives the likelihood horder.    Thus the points-based ordering would be Hamilton, Vettel, R\"{a}ikk\"{o}nen YES I KNOW IT IS WRONG: RMARKDOWN IS DEFECTIVE while the likelihood ordering is (reading vertically) Hamilton, Vettel, Bottas"}
par(pty='s')        # square plot
ox <- dp
oy <- ordertrans(m,dp)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

>>>>

```{r, label=calcpoints, echo=FALSE, cache=TRUE}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points_real <- p
points_inaugural <- c(8,6,4,3,2)
dp2017 <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp2017 <- sort(dp2017,decreasing=TRUE)
dp2017[] <- seq_along(dp2017)
m2017 <- maxp(H2017)
m2017 <- sort(m2017,decreasing=TRUE)
m2017[] <- seq_along(m2017)
```

@@

```{r,label=likevspoints,cache=TRUE,echo=FALSE,fig.cap="Ordering of the \\label{orderingbypointsandlikelihood} top-ranked 11 drivers in the 2017 Formula 1 season.  Horizontal axis gives official (points-based) order, and the vertical axis gives the likelihood horder.    Thus the points-based ordering would be Hamilton, Vettel, R\"{a}ikk\"{o}nen YES I KNOW IT IS WRONG: RMARKDOWN IS DEFECTIVE while the likelihood ordering is (reading vertically) Hamilton, Vettel, Bottas"}
par(pty='s')        # square plot
ox <- dp2017
oy <- ordertrans(m2017,dp2017)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```
